Language-Based Security for Low-Level MPC

### 2024-05-15 ppdp24/main.tex
first folder commit
checkpoint

\documentclass[acmsmall,screen,review]{acmart}

\usepackage{amsmath}
\usepackage{amstext}
\usepackage{fp-frame}
\usepackage[latin1]{inputenc}
\usepackage{mathpartir}
\usepackage{fancyvrb}
\usepackage{moreverb}
\usepackage{stmaryrd}
\usepackage{enumerate}
\usepackage{thmtools,thm-restate}
\usepackage{comment}
\usepackage{booktabs,array}

\input{macros}

@@

\title{Automating Verification of MPC Security: $\metaprot$ to $\minifed$}

\author{Author names withheld for double-blind reviewing}

\begin{abstract}
Secure Multi-Party Computation (MPC) protocols support data privacy in
important modern distributed applications. Security for MPC protocols
is superficially similar to probabilistic noninterference, but differs
in a subtle but fundamental way, and approaches for verifying
noninterference cannot naturally extend to MPC security.  Currently,
proof methods for MPC protocols are well-studied but manual and thus
tedious and error-prone, and are also non-standardized and unfamiliar
to most PL theorists.  Our goal is to leverage connections between the
security model of MPC and trace-based hyperproperties to obtain
automated proof methods for MPC protocol development.  We develop a
language model with a tightly coupled notion of probabilistic program
distributions, as a foundation for fully and partially automated
verification of passive MPC security in protocols including
arbitrarily large YGC and GMW circuits.
\end{abstract}

@@

%%
%% Keywords. The author(s) should pick words that accurately describe
%% the work being presented. Separate the keywords with commas.
\keywords{Secure multiparty computation, security verification, probabilistic programming, static analysis.}

%\maketitle

@@

\input{types}

%\input{scratch}

>>>>

\documentclass[sigconf]{acmart}

\usepackage{amsmath}
\usepackage{amstext}
\usepackage{fp-frame}
\usepackage[latin1]{inputenc}
\usepackage{mathpartir}
\usepackage{fancyvrb}
\usepackage{moreverb}
\usepackage{stmaryrd}
\usepackage{enumerate}
\usepackage{thmtools,thm-restate}
\usepackage{comment}
\usepackage{booktabs,array}
\usepackage{rotating}

\input{macros}
\input{figures}

\acmConference[PPDP]{Principles and Practice of Declarative Programming}{2024}{Milan}

@@

\title{Language-Based Security for Low-Level MPC}

\author{Christian Skalka}
\affiliation{
  \institution{University of Vermont}
  \city{}
  \country{}
%  \city{Burlington}
%  \country{USA}
}
\email{ceskalka@uvm.edu}

\author{Joseph Near}
\affiliation{
  \institution{University of Vermont}
  \city{}
  \country{}
%  \city{Burlington}
%  \country{USA}
}
\email{jnear@uvm.edu}

\begin{abstract}
  Secure Multi-Party Computation (MPC) protocols is an important
  enabling technology for data privacy in modern distributed
  applications. Currently, proof methods for low-level MPC protocols
  are primarily manual and thus tedious and error-prone, and are also
  non-standardized and unfamiliar to most PL theorists. We develop a
  new staged programming language for defining a variety of low-level
  protocols with probabilistic features. We also formulate a
  collection of confidentiality and integrity hyperproperties for our
  language model that are familiar from information flow, including
  conditional noninterference, delimited release, and robust
  declassification. We demonstrate their relation to standard MPC
  threat models of passive and malicious security, and how they can be
  leveraged in security verification of protocols. To prove these
  properties we develop automated tactics in $\mathbb{F}_2$ that
  can be integrated with separation-logic style reason. 
\end{abstract}

@@

%%
%% Keywords. The author(s) should pick words that accurately describe
%% the work being presented. Separate the keywords with commas.
\keywords{Secure multiparty computation, security verification, probabilistic programming, programming languages, information flow.}

\maketitle

\input{intro}

@@

\input{bruteforce}

\input{metalang}

\input{example-gmw}

\input{example-bdoz}
